\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with`a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{PS1}
\author{Paul White}

\begin{document}
\maketitle

\begin{abstract}
Interests in data science and economics.
\end{abstract}

\section{Body}

My interest in data science resulted from my interest in economics and math. My interest in economics goes back a long way, as it's always been interesting to me. It's evolved over time from a naive interest in business and profit as a young one to my interest in the systematic and mathematical nature of economics. Data Science, as a discipline, has come to be necessary in the pursuit of a deeper understanding of the math behind the relationships that drive the economy. In the age of ever accruing information, data science has also become necessary for guiding decision making, and valuable for its application to the vast amount of data available to us now. I wanted to take this course for these very reasons; at this point, I've become quite familiar with data science, yet not yet well-versed in applying it to economics.

I do not yet have a ton of ideas for my project. I think I want to work with something crime related. I've become more interested in using statistical applications with crime statistics. I've also become more passionate about the effects that our judicial system has on people. My goals are to develop a deeper understanding of the specific applications of data science on economics, mostly in the application of economic theory on data.

After graduation, I plan to move to Madison, WI, where I'll be a Solutions Engineer at Epic Healthcare Systems.


\section{Equation}
$$a^2+b^2=c^2$$


\end{document}