\documentclass{article}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[authordate,autocite=inline,backend=biber,sorting=nyt,natbib=true]{biblatex-chicago}
\DeclareUnicodeCharacter{202F}{\,}
\addbibresource{PS11_White.bib}


\title{PS11 White}
\author{Paul White}
\date{April 2022}

\begin{document}

\maketitle

\section{Introduction}

\begin{itemize}
    \item Cultural significance and origin of Pokemon \citep{bainbridge,schmidt, phylogeny}.
    \item Establishment of Pokemon competitive environment, including description of Smogon and Pokemon Showdown \citep{zielke,minmax}.
    \item Examples of complexity of play and AI created for it \citep{huang,minmax,reinforcement,zielke, settings}
    \item Description of complexity of team building \citep{Verdear}
\end{itemize}

\section{Data}

\begin{itemize}
    \item Description of data set (full Pokedex from kaggle.com), and full listing of competitive evaluation from Smogon. Note - data was primarily cleaned in Excel, removing unnecessary variables like the Japanese name (as I can't read Japanese), or Pokedex entry, as well as addition of competitive battle tier.
    \item Descriptive statistics of fully evolved Pokemon, including stats by primary type, abilities, and tier.
    \item Changes over the Pokedex, estimates of Pokemon specialization, especially within tier.
    \item Prediction of competitive tier of 8th generation Pokemon based on 7th generation competitive scene. This will definitely fail to be fully accurate, as there were some significant changes from gen 7 to 8, including the omission of many Pokemon species. Additionally, at present the data set does not consider Mega Evolutions or Gigantimaxes, which are important tactical choices.
    \item Prediction of teams within tiers based on typing, stats and Abilities.
\end{itemize}

\section{Conclusions}

\begin{itemize}
    \item Complexity of decision state
    \item Limitations of models that fail to include competitive player ingenuity and creativity (ex. change in Uber tier meta following the consecutive introductions of Primal Kyogre, Arceus-Grass, followed by Hidden Power Fire Mega Gengar).
    \item Brief discussion of competitive scene over time and potential future decisions.
\end{itemize}

\newpage
\printbibliography

\end{document}
